A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-05 paper/ms.tex
minor ms updtaes

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.5\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Combining
  kinematic information from Gaia, stellar rotation periods from TESS,
  and Li abundances from ground-based spectra, we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster.  To our knowledge, Kepler\,1627Ab is the youngest planet
  with a precise age yet found by the main Kepler mission.  From both
  unresolved starspot-crossing events in the Kepler photometry and
  from a Keck/HIRES transit we find that the planet is
  likely on an orbit nearly aligned with the stellar spin axis.  We
  also find from the short-cadence Kepler photometry that although the
  flare arrival time distribution is probably Poissonian, there may be
  an excess of flares separated by the orbital and synodic periods,
  and linear combinations thereof.  The $\delta$~Lyr cluster is one of
  many stellar groups whose properties have been clarified using the
  Gaia data; many other new clusters also overlap with confirmed and
  candidate exoplanets.  Further studies that combine Gaia kinematics
  and TESS rotation periods are poised to expand the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.5\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short-cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be an effective path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}
